Ionospheric Disturbances in Mexican Territory Produced by Objects Entering the Athmosphere from Space \tnoteref{tnote1}

### 2021-08-10 paper/manuscript.tex
Finished filling out GPS stations table with:
- GPS stations names
- Location
- Citations and references

% Following three lines are needed for this document.
% If you are not loading colors or url, then these are
% not required.
\usepackage{url}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{tablefootnote}
\definecolor{newcolor}{rgb}{.8,.349,.1}

\usepackage[citebordercolor=white]{hyperref}

\journal{Advances in Space Research}

@@

\begin{table*}
  \centering
  \caption{List of meteors passing through Mexico. The events are listed in chronological order. The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites. The uncertainties correspond to the respecting mean deviation.}
\label{tab:table-meteors}
\begin{tabular}{|r|r|r|r|r|r|}
\hline
ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)\\
\hline
01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
06\tablefootnote{This object was only detected by GOES-16 satellite} & 2019-10-12 & 11:12:27 & $0.006\pm 0.0000$ & $28.8 \pm 0.000$ & $-111.3 \pm 0.000$\\
07 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
08 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
09 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
10 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
11 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
12 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
13 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
14 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
15 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
16 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
17 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
18 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
19 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
20 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
21 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
22 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
23 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
24 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
25 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
26 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
27 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
28 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
29 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
30 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
31 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
32 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
33 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
34 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
35 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
\end{tabular}
\end{table*}

@@

For the selected sample, we obtained RINEX data from the TlalocNet \citep{Cabral-Cano:2018} and UNAVCO network databases to study potential alterations in the ionospehre due to the presence of the passing meteor at the day the meteor was reported. For each event, we downloaded data from stations that surrounds the place where the event was detected (usually 3 to 5 stations. )The list of the sample meteors is shown in table \ref{tab:table-meteors}. The events are in chronological order. The reported duration, latitude and longitude correspond to the mean between measurements from satellites GOES-16 and GOES 17; in the same way, the uncertainties correspond to the standard deviation. Also their respective positions are available in figure \ref{fig:meteors-map}, where each label correspond to the ID (first column) of table \ref{tab:table-meteors}.

Using the data provided by TlalocNet and UNAVCO, we procceeded to obtain TEC parameters with the GPS\_GOPI software, available at \url{https://seemala.blogspot.com/}. This software takes as input the RINEX data (the navigation file is no strictly neccesary), and the outuput consists in in the vTEC and sTEC measurements for the PRNs of the whole day the event occurred, as well as the averaged TEC as function of time. We obtained vTEC maps for the events in table (\ref{tab:table-meteors}) and their respective next and previous day.

>>>>

% Following three lines are needed for this document.
% If you are not loading colors or url, then these are
% not required.
\usepackage{url}
\usepackage{xcolor}
\usepackage{multirow}
%\usepackage{tablefootnote}
\definecolor{newcolor}{rgb}{.8,.349,.1}

\usepackage[citebordercolor=white]{hyperref}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage{longtable}
\journal{Advances in Space Research}

@@

\begin{table*}
  \centering
  \caption{List of meteors passing through Mexico. The events are listed in chronological order. The listed duration, latitude and longitude correspond to the mean of the measurements of both GOES satellites. The uncertainties correspond to the respecting mean deviation.}
\label{tab:table-meteors}
\begin{tabular}{rrrrrr}
\hline
ID & Date of event & Start Time (UT)  & Duration (seconds) & Latitude (deg) & Longitude (deg)\\
\hline
01 & 2019-05-23 & 16:36:18 & $0.197\pm 0.0000$ & $24.30 \pm 0.000$ & $-101.60 \pm 0.849$\\
02 & 2019-07-18 & 14:30:30 & $0.058\pm 0.0000$ & $27.20 \pm 0.000$ & $-103.15 \pm 0.778$\\
03 & 2019-08-10 & 11:18:48 & $0.199\pm 0.0757$ & $21.50 \pm 0.000$ & $-102.50  \pm 0.849$\\
04 & 2019-10-03 & 07:55:33 & $0.106\pm 0.0297$ & $25.65 \pm 0.071$ & $-96.25 \pm   0.778$\\
05 & 2019-10-09 & 06:08:11 & $0.103\pm 0.0078$ & $23.60 \pm 0.000$ & $-111.95 \pm  0.212$\\
06 & 2019-11-16 & 09:36:04 & $0.396\pm 0.0134$ & $20.30 \pm 0.000$ & $-100.55 \pm  0.919$\\
07 & 2019-11-17 & 15:36:01 & $0.116\pm 0.0035$ & $31.70 \pm 0.000$ & $-117.70 \pm  1.131$\\
08 & 2019-11-19 & 07:57:40 & $0.097\pm 0.1138$ & $20.00 \pm 0.000$ & $-88.40 \pm  1.131$\\
09 & 2019-11-26 & 13:23:20 & $0.078\pm 0.0290$ & $23.90 \pm 0.000$ & $-108.70 \pm  0.849$\\
10 & 2019-12-04 & 09:42:54 & $0.173\pm 0.0028$ & $31.50 \pm 0.000$ & $-113.65 \pm  0.919$\\
11 & 2019-12-15 & 14:50:49 & $0.127\pm 0.0134$ & $27.70 \pm 0.000$ & $-114.10 \pm  0.849$\\
12 & 2019-12-29 & 16:16:35 & $0.062\pm 0.0134$ & $29.60 \pm 0.000$ & $-116.35 \pm  0.919$\\
13 & 2020-01-03 & 14:10:17 & $0.113\pm 0.0085$ & $30.20 \pm 0.000$ & $-117.65 \pm  0.919$\\
14 & 2020-01-06 & 16:39:27 & $0.118\pm 0.0042$ & $31.40 \pm 0.000$ & $-108.20 \pm  0.990$\\
15 & 2020-01-15 & 15:00:33 & $0.213\pm 0.1351$ & $19.45 \pm 0.071$ & $-95.55 \pm   0.919$\\
16 & 2020-02-12 & 09:25:40 & $0.210\pm 0.0226$ & $18.90 \pm 0.000$ & $-93.50 \pm   0.849$\\
17 & 2020-03-03 & 12:33:27 & $0.062\pm 0.0007$ & $18.25 \pm 0.071$ & $-106.35 \pm 0.636$\\
18 & 2020-03-31 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
19 & 2020-04-08 & 16:25:28 & $0.120\pm 0.0926$ & $26.10 \pm 0.000$ & $-93.90 \pm   0.849$\\
20 & 2020-04-18 & 17:43:25 & $0.139\pm 0.0106$ & $29.00 \pm 0.000$ & $-106.55 \pm  0.919$\\
21 & 2020-04-20 & 16:05:22 & $0.318\pm 0.1655$ & $28.15 \pm 0.071$ & $-97.85 \pm   1.061$\\
22 & 2020-04-25 & 11:03:09 & $0.323\pm 0.0813$ & $32.15 \pm 0.071$ & $-111.60 \pm  1.131$\\
23 & 2020-04-28 & 19:31:52 & $0.105\pm 0.0573$ & $28.45 \pm 0.071$ & $-112.05 \pm  0.636$\\
24 & 2020-05-08 & 10:06:16 & $0.490\pm 0.0750$ & $21.60 \pm 0.000$ & $-92.40 \pm   0.849$\\
25 & 2020-07-15 & 19:58:28 & $0.693\pm 0.0495$ & $24.00 \pm 0.000$ & $-108.35 \pm  0.495$\\
26 & 2020-08-07 & 13:29:57 & $0.163\pm 0.0057$ & $28.80 \pm 0.000$ & $-106.05 \pm  0.919$\\
27 & 2020-09-13 & 16:41:59 & $0.184\pm 0.0078$ & $28.45 \pm 0.071$ & $-113.75 \pm  0.919$\\
28 & 2020-09-30 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
29 & 2020-11-16 & 12:28:11 & $0.100\pm 0.0078$ & $24.90 \pm 0.000$ & $-110.90 \pm  0.849$\\
30 & 2020-11-17 & 12:53:41 & $0.404\pm 0.0262$ & $23.00 \pm 0.000$ & $-102.45 \pm  0.919$\\
31 & 2020-12-19 & 10:18:14 & $0.407\pm 0.0110$ & $21.95 \pm 0.071$ & $-101.60 \pm  0.990$\\
32 & 2020-12-23 & 09:43:01 & $0.148\pm 0.0014$ & $25.75 \pm 0.071$ & $-111.25 \pm  0.778$\\
33 & 2020-12-29 & 15:20:54 & $0.118\pm 0.0014$ & $16.80 \pm 0.000$ & $-102.20 \pm  0.707$\\
34 & 2021-03-31 & 09:01:17 & $0.753\pm 0.3083$ & $20.15 \pm 0.071$ & $-92.95 \pm  0.212$\\\hline
\end{tabular}
\end{table*}

@@

This material is based on services provided by the GAGE Facility, operated by UNAVCO, Inc., with support from the National Science Foundation and the National Aeronautics and Space Administration under NSF Cooperative Agreement EAR-1724794.

We got RINEX data from 3 to 7 stations depending of the event location and data availability that surround the event place in all directions as possible. A list of the stations where we got RINEX data is available in table  . Most of the stations lie in mexican territory, but in some cases we required data from other stations to cover events near the mexican frontier at north or south.

\clearpage
\onecolumn
\begin{landscape}
%\begin{table*}
%    \centering
  \begin{longtable}{lllp{4cm}p{10cm}}
      \caption{List of GPS stations used for this work.}
      \label{tab:table-stations}
      \endfirsthead
      \endhead
    \hline
    Station name & Latitude & Longitude & Date of events  & Citation \\\hline
    BAR1\hyperlink{Hudnut}{${}^1$}\hyperlink{Hudnut2}{${}^5$}& 33.48 & -119.03 & 2019-12-29 2020-01-03 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - BAR1-Santa Barbara Island One P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BHN}.\\
    BLYT\hyperlink{Hudnut}{${}^1$} & 33.61 & -114.71 & 2019-12-29 2020-01-03 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - BLYT-Blythe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5HT2MKK}.\\
    CN23 & 17.26 & -88.78 & 2019-11-19 2020-01-15 2020-02-12& UNAVCO Community, 2012, COCONet GPS Network - CN23-BelmopanBZCR2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q23XJH}.\\
    CN25 & 16.23 & -92.13 & 2020-01-15 & UNAVCO Community, 2014, COCONet GPS Network - CN25-ComitandDMEX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57W69G7}.\\
    GCFS & 19.31 & -81.18 & 2019-11-19& Watts, Anthony, 2016, COCONet GPS Network - GCFS-G\_CAYMAN\_CYM2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/7ETV-X536}.\\
    GMPK\hyperlink{Hudnut}{${}^1$} & 33.05 & -114.83 & 2019-12-04 & UNAVCO Community, Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2005, SCIGN-PBO Nucleus GPS Network - GMPK-Glamis Peak P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/WCHN-H687}.\\
    GUAT\hyperlink{Garnier}{${}^2$} & 14.59 & -90.52 & 2020-02-12 & DeMets, Charles, Cosenza-Muralles, Beatriz, 2021, Central America 2018 - Guatemala, The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/KH2R-K704}.\\
    GUAX\hyperlink{Hudnut}{${}^1$} & 28.88 & -118.29 & 2019-10-09 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-07-15 2020-09-13 2020-09-30 2020-12-23 & Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2001, SCIGN USGS GPS Network - GUAX-Isla Guadalupe P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5GX48T2}.\\
    IAGX & 29.03 & -113.17 & 2019-12-04 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - IAGX-iagxREGNOMmx2018 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/DGWN-A627}.\\
    INEG & 21.85 & -102.28 & 2020-07-15 2020-08-07 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & No citations were found\\
    KVTX & 27.55 & -97.89 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2020-04-08 2020-04-18 2020-04-20 2020-05-08 2020-08-07 & UNAVCO Community, 2007, PBO GPS Network - KVTX-KingsvilleTX2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J38QH8}.\\
    MDO1 & 30.68 & -104.02 & 2019-07-18& No citations were found\\
    MGO5 & 30.68 & -104.02 & 2020-04-20 2020-08-07 & No citations were found\\
    MGW3 & 29.62 & -89.95 & 2020-04-08 2020-04-20 2020-05-08 & No citations were found\\
    OXTH & 16.29 & -95.24 & 2020-01-15 2020-02-12 & DeMets, Charles, Cabral-Cano, Enrique, 2008, Oaxaca GPS Network - OXTH-Tehuantepec P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5Q81B5V}.\\
    OXUM\hyperlink{Graham}{${}^3$} &  &  & 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - OXUM-oxum\_tnet\_mx2001 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5J964RP}.\\
    P001 & 31.95 & -112.80 & 2020-04 25 & UNAVCO Community, 2008, PBO GPS Network - P001-Organ\_PipeAZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DR2SGP}.\\
    P014 & 31.97 & -11.09 & 2019-12-04 2019-12-29 2020-01-03 2020-01-06 2020-04-25 & UNAVCO Community, 2008, PBO GPS Network - P014-Sahuarita\_AZ2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5CMK}.\\
    P807 & 30.49 & -98.82 & 2019-11-17 2020-01-06 2020-04-20 2020-11-17 & UNAVCO Community, 2012, PBO GPS Network - P807-EcRockStPkTX2012 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5TQ5ZKM}.\\
    PLPX & 31.59 & -115.15 & 2019-12-04 & UNAVCO Community, 2011, PBO GPS Network - PLPX-Las\_PintasMX2010 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5K64G3T}.\\
    PTEX & 32.29 & -116.52 & 2019-12-29 2020-01-03 2020-09-13 2020-12-23 & UNAVCO Community, 2011, PBO GPS Network - PTEX-Testerazo\_MX2011 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XBP}.\\
    RG06 & 32.63 & -107.86 & 2020-04-25 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG06-RG06FaywodNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5668BFR}.\\
    RG07 & 32.50 & -106.84 & 2020-01-06 & Sheehan, Anne, 2007, Rio Grande Rift GPS Network - RG07-RG07CrucesNM2006 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KD1W45}. \\
    SG33 & 31.77 & -106.51 & 2019-11-17 2020-04-18 2020-08-07 & Harder, Steven, Kaip, Galen, Montana, Carlos, 2004, SuomiNet-G GPS Network - SG33-UTEP P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50863KQ}.\\
    TGMX  & 20.87 & -86.87 & 2021-03-31 & UNAVCO Community, 2015, COCONet GPS Network - TGMX-PtoMor\_TG\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5154FB7}.\\
    TNAM & 20.54 & -103.97 & 2020-03-03 2020-07-15 2020-09-30 2020-11-16 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNAM-TNAM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5QF8R4R}.\\
    TNAT & 18.13 & -98.04 & 2020-01-15 & UNAVCO Community, 2014, TLALOCNet - TNAT-TNAT\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5G15Z4S}.\\
    TNBA & 28.97 & -113.55 & 2019-10-09 2019-11-26 2019-12-15 2019-12-29 2020-01-03& UNAVCO Community, 2015, TLALOCNet - TNBA-TNBA\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T57M0688}.\\
    TNCC & 18.79 & -103.17 & 2020-03-03 & UNAVCO Community, 2015, TLALOCNet - TNCC-TNCC\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T50R9MSK}.\\
    TNCM & 19.50 & -105.04 & 2020-03-03 2020-04-28 & UNAVCO Community, 2014, TLALOCNet - TNCM-TNCM\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5B856FW}.\\
    TNCN & 18.55 & -101.97 & 2020-11-16 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNCN-TNCN\_TNET\_MX2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5610XQM}.\\
    TNCU & 28.45 & -106.79 & 2019-05-23 2019-07-18 2019-08-10 2019-11-17 2019-12-15 2020-01-06 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-11-17 2020-12-19 & UNAVCO Community, 2014, TLALOCNet - TNCU-CuauhtemocTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5V69GV2}.\\
    TNGF & 19.33 & -99.18 & 2020-11-16 2020-12-29 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2016, TLALOCNet GPS Network - TNGF\_Geofisica-UNAM\_Mexico\_City\_TNET\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53X851M}.\\
    TNHM & 29.08 & -110.97 & 2019-10-09 2019-11-26 2019-12-04 2019-12-15 2019-12-29 2020-01-03 2020-03-31 2020-04-18 2020-07-15 2020-08-07 2020-09-13 2020-09-30 2020-12-23 & UNAVCO Community, 2014, TLALOCNet - TNHM-hermosilloTN2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5KP80FV}.\\
    TNMS & 20.53 & -104.80 & 2019-10-09 2019-11-26 2019-12-15 2020-03-03 2020-07-15 & UNAVCO Community, 2014, TLALOCNet - TNMS-TNMS\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T56H4FQ5}.\\
    TNNP & 16.12 & -97.14 & 2020-04-28 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, DeMets, Charles, 2016, TLALOCNet - TNNP-tnnp\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5N29V96}.\\
    TNNX & 17.41 & -97.22 & 2020-01-15 2020-02-12 2020-12-29 2021-03-31 & UNAVCO Community, 2014, TLALOCNet - TNNX-TNNX\_TNET\_MX2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T52R3PZ0}.\\
    TNPP & 31.34 & -113.63 & 2019-12-04 2020-03-31 2020-04-25 & UNAVCO Community, 2015, TLALOCNet - TNPP-TNPP\_TNET\_MX2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5CC0Z0M}.\\
    TNSJ & 16.17 & -96.49 & 2020-12-29 & UNAVCO Community, 2016, TLALOCNet - TNSJ-tnsj\_tnet\_mx2015 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59S1PF1}.\\
    TSFX & 30.93 & -114.81 & 2020-09-13 2020-12-23 & Gonzalez-Ortega, Alejandro, Galetzka, John E., Gonzalez, Javier, 2018, CICESE REGNOM GPS Network - TSFX-tsfxREGNOMmx2016 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/AGEA-2G27}.\\
    UAGU & 21.92 & -102.32 & 2019-05-23 2019-07-18 2019-08-10 2019-10-03 2019-11-17 2019-11-26 2019-12-15 2020-04-18& Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UAGU-uagu\_tnet\_mx2008 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5513WK7}.\\
    UCOE\hyperlink{Graham}{${}^3$} & 19.81 & -101.69 & 2019-08-10 2020-11-16 2020-11-17 2020-12-19 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UCOE-ucoe\_tnet\_mx2003 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T51834VW}.\\
    UGEO\hyperlink{Marquez}{${}^4$} & 20.69 & -103.35 & 2019-08-10& Marquez-Azua, Bertha, DeMets, Charles, Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UGEO-ugeo\_tnet\_mx1998 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T58S4N9N}.\\
    UHSL & 29.57 & -95.65 & 2020-04-08 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHSL-SugarLandUSA2014 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T55X271S}.\\
    UHWL & 30.06 & -94.98 & 2020-12-19 & Wang, Guoquan, 2014, HoustonNet GPS Network - UHWL-West Liberty Airport(Deep) P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T53R0R5P}.\\
    UNPM & 20.86 & -86.86 & 2019-11-19 2020-01-15 2020-02-12 2020-05-08 & UNAVCO Community, 2012, COCONet GPS Network - UNPM-Puerto\_Morelos\_MX\_2007 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/J1GD-5S40}.\\
    USMX & 29.82 & -109.68 & 2019-12-29 2020-01-03 2020-01-06 2020-04-25 2020-08-07 2020-09-30& Bennett, Rick, 2004, Northwest Mexico GPS Network - USMX-Universidad de la Sierra P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5W957CQ}.\\
    UXAL\hyperlink{Graham}{${}^3$} &  &  & 2019-10-03 2020-01-15 2020-02-12 2020-04-08 2020-05-08 2020-12-19 2021-03-31 & Cabral-Cano, Enrique, Salazar-Tlaczani, Luis, 2015, TLALOCNet - UXAL-uxal\_tnet\_mx2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5DJ5D1C}.\\
    WEPD & 29.69 & -95.23 & 2020-04-20 & Wang, Guoquan, 2014, HoustonNet GPS Network - WEPD-willmselementary P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5NZ85RB}.\\
    WMOK & 34.74 & -98.78 & 2020-04-20 & UNAVCO Community, 2005, PBO GPS Network - WMOK-WichitaMtnOK2005 P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T59021Q6}.\\
    WWMT\hyperlink{Hudnut}{${}^1$} & 33.96 & -116.65 & 2019-12-29 2020-01-03& Hudnut, Kenneth, King, Nancy, Aspiotes, Aris G., Borsa, Adrian A., Determan, Daniel N., Galetzka, John E., Stark, Keith F., 2006, SCIGN USGS GPS Network - WWMT-Whitewater Mountain P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5H993F2}.\\
    YESX & 28.38 & -108.92 & 2019-11-26 2019-12-15 2020-01-06 2020-04-18 2020-04-28 2020-07-15& Bennett, Rick, 2004, Northwest Mexico GPS Network - YESX-Yecora P.S., The GAGE Facility operated by UNAVCO, Inc., GPS/GNSS Observations Dataset, \url{https://doi.org/10.7283/T5RJ4GPF}.\\\hline
    % \end{table*}
  \end{longtable}
    \begin{minipage}{0.9\linewidth}
      \footnotesize
      Related articles:

      \hypertarget{Hudnut}{${}^1$}\citet{Hudnut:2002},
      %
      \hypertarget{Garnier}{${}^2$}\citet{Garnier:2021}, 
      %
      \hypertarget{Graham}{${}^3$}\citet{Graham:2016}

      \hypertarget{Marquez}{${}^4$}\href{https://doi.org/10.7283/T58S4N9N}{B. Marquez-Azua, E. Cabral-Cano, F. Correa-Mora and C. DeMets, 2004. A model for Mexican neotectonics based on Nationwide GPS measurements, 1993-2001, Geofisica Internacional, v. 43, p.319-330}

      \hypertarget{Hudnut2}{${}^5$}\href{https://doi.org/10.7283/T5668BHN}{Hudnut, K. W., Y. Bock, J. E. Galetzka, F. H. Webb, and W. H. Young, The Southern California Integrated GPS Network (SCIGN), Proceedings of the International Workshop on Seismotectonics at the Subduction Zone, Y. Fujinawa (ed.), NIED, Tsukuba, Japan, pp. 175-196, 1999}
